% academic-cv.tex - format fixture: CV with academic \section headings, ~2 pages.
% Tests CV recognition (Publications/Grants/Teaching are in DOC_SECTIONS) and the
% --pages 0 natural-length fit. Expected: check flags it as a resume/CV;
% --pages 0 fits its natural length (2 pages).
\documentclass[letterpaper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{xfp}
\usepackage{enumitem}
\usepackage{titlesec}
\newcommand{\rs}{1.000}
\newcommand{\fs}[2]{\fontsize{\fpeval{#1*\rs}}{\fpeval{#2*\rs}}\selectfont}
\newcommand{\sv}[1]{\vspace{\fpeval{#1*\rs}pt}}
\titleformat{\section}{\fs{13}{16}\bfseries}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{\fpeval{7*\rs}pt}{\fpeval{3*\rs}pt}
\setlength{\parindent}{0pt}\pagestyle{empty}
\begin{document}
{\fs{22}{26}\bfseries Dr. Sam Ortiz}\\[2pt]
{\fs{10}{13} Assistant Professor of Biomedical Informatics \textbullet\ sam.ortiz@example.com}

\section{Research}
{\fs{11}{14} Computational methods for large-scale health data, reproducible
analytics, and data-quality measurement across clinical systems.}

\section{Education}
{\fs{11}{14}\bfseries PhD, Biomedical Informatics}, University of Example, 2017\\
{\fs{11}{14}\bfseries BS, Computer Science}, University of Example, 2012

\section{Publications}
\begin{enumerate}[leftmargin=1.5em,itemsep=3pt]
\item Ortiz S., Lee J., Nair P. A scalable pipeline for clinical cohort discovery. Journal of Example Informatics, 2024.
\item Ortiz S., Kim C. Reproducibility in health analytics: a survey. Example Data Review, 2023.
\item Ortiz S. Measuring data quality at scale. Proceedings of Example Conference, 2022.
\item Ortiz S., Brooks T. Standardizing quality measures across systems. Example Health Journal, 2021.
\item Ortiz S. et al. A framework for auditable data pipelines. Example Systems, 2020.
\item Ortiz S., Reyes M. Cohort reproducibility benchmarks. Example Informatics Letters, 2019.
\item Ortiz S., Nair P. Automated validation for research data. Example Methods, 2018.
\item Ortiz S. Toward transparent analytics workflows. Example Review, 2017.
\item Ortiz S., Lee J. Scaling data quality checks. Example Proceedings, 2016.
\end{enumerate}

\section{Grants}
\begin{itemize}[leftmargin=1.5em,itemsep=3pt]
\item Example Foundation Research Award, Principal Investigator, 2023 to 2026.
\item National Example Institute Pilot Grant, Co-Investigator, 2021 to 2022.
\item Institutional Seed Fund, Principal Investigator, 2019.
\end{itemize}

\section{Teaching}
\begin{itemize}[leftmargin=1.5em,itemsep=3pt]
\item Graduate Data Management and Governance, instructor of record, 2022 to present.
\item Introduction to Statistical Computing, 2020 to 2022.
\item Guest lectures, Reproducible Research seminar, annually since 2019.
\end{itemize}

\section{Presentations}
\begin{itemize}[leftmargin=1.5em,itemsep=3pt]
\item Invited talk, Example Analytics Summit, 2024.
\item Panelist, Reproducible Research Workshop, 2023.
\item Poster, Example Informatics Conference, 2021.
\end{itemize}

\section{Service}
\begin{itemize}[leftmargin=1.5em,itemsep=3pt]
\item Reviewer, Journal of Example Informatics and Example Data Review.
\item Committee member, departmental data governance working group.
\item Mentor, undergraduate research program, 2020 to present.
\end{itemize}

\end{document}
